Gaia's constraints on the $\sim$$150\,M_\odot$ runaway star candidate VFTS682

### 2018-06-09 VFTS682_APJL.tex

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.5\textwidth]{figures/dist_mu_region.pdf}
  \caption{Distribution of OB-type and Wolf-Rayet stars in proper
    motion relative to R136. VFTS682 is not an extreme outlier, but
    its relative proper motion matches the expected value if it were indeed
    ejected from R136 assuming an age of $1.0\pm0.2$\,Myr. The dark blue histogram contains 317 
    stars with error smaller than $0.1\,\mathrm{mas \
      yr^{-1}}\simeq25\,\mathrm{km\ s^{-1}}$ at 50\,kpc, the
    lighter blue histogram contains 36 stars with errors smaller than $0.05\,\mathrm{mas \
      yr^{-1}}$.}
  \label{fig:mu_dist}
\end{figure}

>>>>

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.5\textwidth]{figures/dist_mu_region.pdf}
  \caption{Distribution of OB-type and Wolf-Rayet stars in proper
    motion relative to R136. VFTS682 is not an extreme outlier, but
    its relative proper motion matches the expected value if it were indeed
    ejected from R136 assuming an age of $1.0\pm0.2$\,Myr. The dark blue histogram contains 317 
    stars with error smaller than $0.1\,\mathrm{mas \
      yr^{-1}}\simeq25\,\mathrm{km\ s^{-1}}$ at 50\,kpc, the
    lighter blue histogram contains 36 stars with errors smaller than $0.05\,\mathrm{mas \
      yr^{-1}}$. The top axis shows the conversion to physical units
    assuming a distance of 50\,kpc.}
  \label{fig:mu_dist}
\end{figure}
